|

### 2024-07-12 doc/paper_mine.qmd
Final commit

Assignment I aims to replicate an empirical table that involves calculating the residual income of US firms over a defined period and examining the relationship between residual income and the Price-to-Book (P/B) ratio. The replication process includes data preparation, cleaning, normalization, and the application of statistical methods to compute and interpret financial metrics using Python. By following a step-by-step approach, I provide insights into the trends of residual earnings across different P/B groups, identical to trends presented by @Penman_2013. This document presents the analysis performed in Assignment I, adapted to the open science workflow. Note that intermediate check steps have been omitted for brevity. The full code, including intermediate print steps to verify outputs, is presented in `code/python/Assignment1_analyze_residual_income.py`.

@@

The aim of Assignment I is to replicate a specific empirical table that involves calculating the residual income of US firms over a defined period and examining the relationship between residual income and the Price-to-Book (P/B) ratio. The replication process involves data preparation, cleaning, and normalization, followed by the application of statistical methods to compute and interpret financial metrics. For Assignment I, I used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

@@

In the future, this repository can be cloned or forked (if made public) to kickstart further projects on residual income analysis. Thanks for reading and enjoy!

>>>>

Assignment I aims to replicate an empirical table that involves calculating the residual income of US firms over a defined period and examining the relationship between residual income and the P/B ratio. The replication process includes data preparation, cleaning, normalization, and the application of statistical methods to compute and interpret financial metrics using Python. By following a step-by-step approach, I provide insights into the trends of residual earnings across different P/B groups, identical to trends presented by @Penman_2013. This document presents the analysis performed in Assignment I, adapted to the open science workflow. Note that intermediate check steps have been omitted for brevity. The full code, including intermediate print steps to verify outputs, is presented in `code/python/Assignment1_analyze_residual_income.py`.

@@

The aim of Assignment I is to replicate a specific empirical table that involves calculating the residual income of US firms over a defined period and examining the relationship between residual income and the P/B ratio. The replication process involves data preparation, cleaning, and normalization, followed by the application of statistical methods to compute and interpret financial metrics. For Assignment I, I used the Python programming language to carry out the empirical analysis. Visual Studio Code was used as the Integrated Development Environment (IDE) for writing, debugging, and optimizing the Python code.

@@

In the future, this repository can be cloned or forked (if made public) to kickstart further projects on residual income analysis. Thanks for reading!
